Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-03-27 document/ms.tex
some notes in the generalities section

From our perspective, a ``model'' is a likelihood function---a probability
density (or distribution) function (PDF) for the data given
parameteters---and a set of prior PDFs for the parameters.
In what follows, we will treat as ``data'' a certain set of exoplanet period
and radius measurements (\citealt{petigura}).
We will treat the uncertainties on those measurements as ``prior
information''; that is, we will treat those as true as given and not as being
generated by the parameterized likelihood function.

In the models that follow, the most important parameters will be parameters
of the PDF for the exoplanet periods and radii.
However, there will also be ``latent parameters'' that represent the ``true''
values of the exoplanet periods and radii.
That is, for each exoplanet, there is a ``measured'' or ``observed'' period
and radius, which constitute our data.
These relate to the unobserved ``true'' period and radius by a noise model.
For the conclusions of this study, the true values of period and radius are
nuisance parameters; we will marginalize them out.

@@

We have some parametric function \rate\ describing the true rate of exoplanets
with periods \period\ and radii \radius
\begin{eqnarray}\eqlabel{true-rate}
\rate (\period,\,\radius;\,\ratepars)
&=& \frac{\dd N}{\dd\ln\period\dd\ln\radius}\quad.
\end{eqnarray}
Here we have not made any assumptions about the functional form of \rate, we
are only stating that it can be modeled by some---possibly very large---set of
parameters \ratepars.

In this \paper, we will assume that the completeness function of the survey is
known and it can be represented as a probability at every period and radius
$\completeness (\period,\,\radius)$.
Similarly, we can consider the marginalized transit probability $\transitprob
(\period)$ as only a function of period.
These selection effects can be incorporated into the rate from \eq{true-rate}
to get the \emph{observed rate}
\begin{eqnarray}\eqlabel{obs-rate}
\obs{\rate} (\period,\,\radius;\,\ratepars)
&=& \rate (\period,\,\radius;\,\ratepars)\,\completeness(\period,\,\radius)\,
\transitprob(\period)\quad.
\end{eqnarray}

>>>>

@@

From our perspective, a ``model'' is a likelihood function---a probability
density (or distribution) function (PDF) for the data given
parameteters---and a set of prior PDFs for the parameters.
In what follows, we will treat as ``data'' a catalog of exoplanet period
and radius measurements (\citealt{petigura}).
\emph{(I don't think need this next sentence).}
We will treat the uncertainties on those measurements as ``prior
information''; that is, we will treat those as true as given and not as being
generated by the parameterized likelihood function.

In the models that follow, the most important parameters will be parameters
of the PDF for the exoplanet periods and radii.
However, there will also be ``latent parameters'' that represent the ``true''
values of the exoplanet periods \period\ and radii \radius.
That is, for each exoplanet, there is a ``measured'' or ``observed'' period
\obs{\period}\ and radius \obs{\radius}, which constitute our data.
These relate to the unobserved ``true'' period and radius by a noise model.
For the conclusions of this study, the true values of period and radius are
nuisance parameters; we will marginalize them out.

The purpose of this \paper\ is to determine constraints on the \emph{rate
function} of exoplanets
\begin{eqnarray}\eqlabel{true-rate}
\rate_\ratepars (\period,\,\radius)
&=& \frac{\dd N}{\dd\ln\period\dd\ln\radius}
\end{eqnarray}
given our dataset.
Here we have not made any assumptions about the functional form of \rate, we
are only stating that it can be modeled by some---possibly very large---set of
parameters \ratepars.

In this \paper, we will assume that the completeness function of the survey is
known and it can be represented as a probability at every (true) period and
radius $\completeness (\period,\,\radius)$.
Similarly, we can consider the marginalized transit probability $\transitprob
(\period)$ as only a function of period.
These selection effects can be incorporated into the rate from \eq{true-rate}
to get the \emph{observed rate}
\begin{eqnarray}\eqlabel{obs-rate}
\obs{\rate} (\period,\,\radius;\,\ratepars)
&=& \rate (\period,\,\radius;\,\ratepars)\,\completeness(\period,\,\radius)\,
\transitprob(\period)\quad.
\end{eqnarray}
